Group 1: Tennis 

### 2019-12-11 Group1Prez.Rmd
just ignore these
Merge branch 'master' of https://github.com/stat400-csu/project_1

# Conflicts:
#	Group1Prez.Rmd
#	Group1Prez.aux
#	Group1Prez.nav
#	Group1Prez.pdf
#	Group1Prez.snm
#	funs.R

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("funs.R")
library(knitr)
options(kableExtra.latex.load_packages = FALSE) 
library(kableExtra)
library(tidyverse)
set.seed(400)
```

>>>>

```{r setup, include=FALSE, warning=FALSE}
source("funs.R")
library(knitr)
options(kableExtra.latex.load_packages = FALSE) 
library(kableExtra)
library(tidyverse)
set.seed(400)
```
